### 2018-01-08 1st_round_comments/1st_round_comments_final/feb02_comments.tex

1) Eq. 2.1, p.16: The second row is missing the charge, q, in front of Bz. This 
is not trivial, as the next 3 lines contain numerical examples that seem to be 
wrong. For instance, the range in $r_{0}$ quoted for DVCS is 20 - 45 mm - but I 
find a radius of 100 mm for 260 MeV/c 4He nuclei going radially (q = 2e). Even 
at some angle, 20 mm is impossible - such a track would never make it through 
the drift region. (Fig. 2.7 shows a minuscule pedestal below $r_{0}$ = 25 mm, but 
this must be due to some spurious effect - I don't see how you can reconstruct 
any tracks with $r_{0}$ < 30 mm). Is this mistake in your software as well (see 
horizontal scale in Fig. 2.7)?\\
\textcolor{blue}{
   In equation 2.1, the charge of the particle (q) is missed. Regarding the 
numerical calculations of $r_0$ for the elastic and the DVCS $^4$He, the 0.3 
factor is missed only in these calculations while the charge issue is taken 
into account. In the reconstruction software, both issues are properly 
implemented.  (For example, In a magnetic field of 4.5 T, the recoil 4He nuclei 
from DVCS (elastic) reaction have kinetic energies in the range [10, 25] ([17, 
35]) MeV, from momenta of [260, 450] ([360, 550]) MeV and $r_0$ [70, 150] 
([130,180]) mm.) }\\

2) Section 2.2: The RTPC calibration procedure is described in 2 steps: Event 
selection (2.2.1) and actual calibration (2.2.2 - 2.2.4) plus noise rejection 
(2.2.5). However, the event selection contains cuts on $r_0$, chi2, z etc.  
which in turn presuppose some initial calibration already. In other words, the 
process MUST be iterative - but I couldn't find a clear summary how this 
iteration was executed (i.e., what was used for the first iteration, how many 
iterations total, etc.). There is a short mention at the bottom of p. 27, but 
no details.\\
\textcolor{blue}{The drift paths and drift speed were first extracted using the 
MAGBOLTZ Monte Carlo simulation. One can find the detailed procedure of 
this first extraction in the BoNuS analysis note 
(https://www.jlab.org/Hall-B/secure/bonus/publication/BonusAnal110117.pdf).  
Then, we proceeded to derive empirical improvements with many iterations after 
each change that would affect the drift paths, such as the beam-offset
 and gain calibrations of the RTPC. Moreover after each pass, the number of
elastic events used for calibration increased. Overall, this was a long 
process that evolved and improved over the years and we concentrated in the 
note on the description of the final iteration.}\\

3) 2.2.1.1 It would be helpful to have some more background information: What 
is the longest drift time (from the inner radius) for a good track? What kind 
of momentum gives you only 4 hits, and are those events important? (see further 
down, under Fig. 3.19) What is the timing offset between the trigger and the 
shortest drift time (outer radius RTPC)? What is the average drift velocity and 
Lorentz angle? Conversion TDC-> time is given p. 15, but it would be much more 
helpful to have all these basic parameters collected in a single place: 2.1.1 - 
2.1.3 are all good places to summarize these parameters.\\
\textcolor{blue}{
  The longest drift time depend on $z$ but is typically around 6.6 $\mu$s. 
  Four is the number of the fired pads for each track, not the number of hits.  
  This value has been found to be reasonable from simulation, it mainly help 
  clean the sample and play very little role after other cuts. The time offset 
  is 15 TDCs (1 TDC= 114 ns), the average drift velocity is 6.14 $\mu$m/ns and 
  we did not extract the Lorentz angle, but MAGBOLTZ indicated about 20 
  degrees.}\\

@@

5) 4th bullet: How are the points $r^{helix}$, $\phi^{helix}$ and $z^{helix}$ 
determined?  Somehow, you have to identify points on a continuous line that are 
closest to (perhaps) the hits? How are the uncertainties (sigmas) in  
$\chi^{2}$ determined?  Are those the final values AFTER calibration? If so, 
how do you select your sample initially? (See above - it must be an iterative 
process).  \\
\textcolor{blue}{$(r^{helix},\phi^{helix},z^{helix})$ is the point
on the helix that is closest to the reconstructed hit position.
The values of the uncertainties are intrinsic detector properties depending
primarily on the size and configuration of the readout pads. These 
uncertainties, $(\sigma_{r}, \sigma_{\phi}, \sigma_{z}) = (0.53 mm, 2^{\circ}, 
1.2 mm)$, were not derived from our data and were held fixed.} \\

\textcolor{blue}{Equation 2.2 needs the beam-spot constraint added in
quadrature $\left(\frac{DOCA}{\sigma_r}\right)^2$ and the denominator adjusted
accordingly $(N_{pts}-5)$. It has to be written in full form as: (changed in 
the note as well).  }\\

\textcolor{blue}{
\begin{equation}
   \chi^{2} = \frac{\displaystyle \left(\frac{DOCA}{\sigma_r}\right)^2 
       + \sum_{i = 1}^{ N_{pts}} \left(\frac{r^{pt}_{i} 
      - r^{helix}_{i} }{\sigma_{r}}\right)^{2}  + \left( \frac{\phi^{pt}_{i} - 
      \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
      z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 5}
\end{equation}
}\\
%  \textcolor{green}{Raph: I did a minor change in the equation, to clarify 
%  that the beam spot term is not in the sum. To use in the note if you are 
%  ok.} \\

@@

14) Figs. 2.20-22: Again, more detail needed to understand what's plotted and 
how it is calculated. Why is Delta-phi not zero for TDC = 15 (which corresponds 
to the outer radius of the drift region)?- Eq. 2.9: A (brief) derivation would 
help a lot here.\\
\textcolor{blue}{
$\Delta \phi$ at the anode (TDC = 15) is not equal to zero because there is a 
drift in phi between the anode (the first GEM layer at radial distance equal to 
60 mm) and the readout pads (at radial distance equal to 69mm). Regarding the 
derivation, figure \ref{fig:drift_derive} shows a simple drawing explaining how 
Eq. 2.9 has been derived.}\\
\textcolor{green}{Raph: Equations in the drawing need to be replaced by text.}

@@

15) 2.2.4: Eq. 2.12 is differential, while Eq. 2.14 is integrated over the 
whole track. Do you integrate Eq. 2.12? Otherwise, it probably doesn't work all 
that well. Maybe this is the reason why the bands visible in Fig. 2.29 are not 
well represented by the superimposed curves? BTW, what is the vertical scale on 
Fig. 2.29?\\
\textcolor{blue}{Eq. 2.14 represents the average energy loss per unit of length in the 
track, $vtl$ being the visible track length. Assuming the energy loss in the 
drift region small, the two can be easily compared. Indeed at the lowest energy 
this assumption is not true anymore. But the difference between instantaneous 
and average $\frac{dE}{dx}$ is expected to be small compared to our 
resolution except very close to threshold (see right panel of Figure 
\ref{fig:energylosscorrection}).}
\textcolor{blue}{In Fig. 2.29 the bands are just there to guide the eye. Since the
vertical scale has never been carefully calibrated, we always present it in
arbitrary units. To have a feeling of the units, we have extracted an over all 
conversions from comparing real data to simulation, where 1 ADC is equal to 17 eV 
(21 eV) deposited in the left (right) module of the RTPC.} \\

16) p. 29, 2nd to last paragraph: I THINK I understand the Landau fit (over 
many tracks, no?) for each channel. But I don't understand the last step - why 
is it needed? What does it accomplish? For sure more details (and a plot) are 
needed.\\
\textcolor{blue}{
Yes, the gain ratio of each readout pad is calculated from comparing all the 
experimental elastic tracks to their corresponding tracks obtained from 
simulation. These ratios give us a first gain for each readout pad. However, 
we noticed that some pads record lower ADCs than expected (issue shown in 
figure 2.28) and noise. For these reasons, we wanted to make sure that the recorded 
ADCs by a given pad are similar to the recorded ADCs recorded by another pad in 
the same track. In figure~\ref{fig:dedxre}, one can see improvements obtained
by using this method to fine tune the gains obtained previously.} \\

\begin{figure}[!h]
\hspace{-0.5 cm}
\includegraphics[height=11.5cm]{fig/dedx_ratio_elastic.png}
\caption{The ratio between experimental dEdx and 
the simulated ones for different regions along $z$ of the RTPC. The blue lines 
are using the first method of extracting the gains (comparing the experimental 
recorded dEdx to the expected values calculated from the Bethe-Block formula), 
the violet lines are using the second method with a small fraction of our 
elastic events, the green lines are using the 1st pass of the second method 
(comparing simulation to data only) with all the elastic event sample and the 
brown lines are using the gains extracted from the second method (both steps).}
\label{fig:dedxre}
\end{figure}

@@

26) Fig. 3.15: This may be my ignorance, but it looks like there is a 
secondary 'bump' between beta =0.9 and 1. What could it be? If it's neutrons, 
wouldn't that contribute to your background?\\
\textcolor{blue}{We seem to disagree there is a significant bump. However, if 
   there are some neutrons, they will be well removed by the following 
   exclusivity requirements. Also we want to point out the energy of the 
   neutral particle we use are greater than 2 GeV.  At such energies the time 
   of flight measurement from the EC is not good enough to separate neutrons 
   from photons anyway (see Fig.  \ref{fig:sim_coh} and 
\ref{fig:sim_incoh}).}\\

27) Bottom p.47: Indicate that the threshold on IC discris towards TDC has been 
too high to be useful and/or the flight path is too short to apply a beta cut 
as in EC.\\
\textcolor{blue}{
 The timing of the IC has is not functionning properly for certain channels. Therefore, 
 applying a timing cut would add inefficient regions in the detector that we 
 wanted to avoid. Moreover, the comment from previous answer applies as well,
such a cut would be very little help to reduce backgrounds at such high particle energies.}\\

28) Fig. 3.19:  The lhs of the RTPC apparently has only 1/2 the efficiency of the 
rhs. Is there any good explanation (at least qualitatively)? This could 
potentially distort phi-distributions, no? \\
\textcolor{blue}{This plot contains no good
   track cuts and so say very little about the efficiency. In more details, 
   This difference in the yield should not be linked to a different performance 
   of the RTPC.  They are due to the complicated convolution of CLAS and the 
   RTPC acceptance.  We measured the efficiency of RTPC using elastic 
scattering, and found that the left/right halves have similar efficiencies 
except near the upstream and downstream ends, as shown in 
Figure~\ref{fig:tpceff}.} \\

@@

\textcolor{blue}{ Regarding the background, figure 
\ref{fig:delta_z_after_exclusitivty} shows $\Delta z$ distributions of the 
identified Coherent DVCS events after applying the exclusivity cuts without any 
initial constrain on $\Delta z$.}\\

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/rtpc_delta_z.png}
\caption{The z-vertex correspondence between the scattered electron and the 
recoil He4 for the identified coherent DVCS events after the exclusivity cuts 
in the two modules of the RTPC separately. Table \ref{table:Events_numbers} 
summarizes the cut numerically. }
\label{fig:delta_z_after_exclusitivty}
 \end{figure}

\begin{table}[!h]
   \centering
   \begin{center}
      \begin{tabular}{|l|l|l|}
         \hline
         \multicolumn{3}{ |c| }{Number of coherent DVCS events} \\
         \hline
         $\Delta z$ [mm] & Left module & Right module\\
         \hline
         [-50:-20] & 165 & 132 \\
         \hline
         [-20:20]  & 2736 & 2828\\
         \hline
         [20:50]   & 78 &  166 \\
         \hline
         Total     & 2979  & 3126 \\
         \hline 
      \end{tabular}
      \caption{The numbers of the identified coherent DVCS events in the 
      different regions in $\Delta z$ for the two modules of the RTPC.}
      \label{table:Events_numbers}
   \end{center}
\end{table}

@@

34) Also in 3.2.5, I would like a little more detail on the fastmc: How does it 
calculate the energy loss of the 4He? Is multiple scattering included? Could 
you show comparisons between measured and simulated distributions?\\
\textcolor{blue}{We do not specifically apply energy loss and multiple 
scattering in our fastmc, but we apply resolution effects based on 
experimental data that include both effects. The plots in Fig.~\ref{fig:comp_He} 
show the comparison between data and simulation in terms of theta, phi and 
momentum of the He-4 DVCS nuclei.}\\

@@

35) 3.3.: The kinematic corrections you mention are based on simulation only and 
mostly take care of energy loss by the protons. Most other CLAS analyses 
require additional, EMPIRICAL kinematic corrections (see, e.g. the BONuS 
experiment). Can you give a justification for leaving them out?
It may be obvious, but you don't show or say it: Are the corrections explained 
in 3.3.1-3.3.3 applied to the real data as well?\\
\textcolor{blue}{For electrons and protons, the presented corrections in 
sections 3.3.1 and 3.3.2, respectively, are applied for experimental data and 
simulation. We did not find the need for additional kinematic corrections on 
protons and electron as we found good enough match already.
In the case of the of the IC photons, the corrections 
for data and for simulation are different and presented in the following two 
sections, sections 3.3.3 and 3.3.4. In the latter case
these where empirical corrections.  Additional corrections are not pursued
for the data since data and simulation already agree reasonably well regarding
the quantities that are involved in event selection and asymmetry 
extraction.}\\

36) 3.3.4: The 3 corrections you describe for IC photons are somewhat 
correlated, since they all are checked by optimizing $m_{\pi^0}$. Did you try a 
simultaneous fit of all parameters (or at least several ones) that enter the 
various corrections?\\
\textcolor{blue}{The position correction (3.3.4.2) is derived based on minimizing
$z$-dependence of $m_{\pi^0}$, and is highly uncorrelated with energy 
corrections. The run-dependence (3.3.4.1) is also uncorrelated with energy, as
can be seen in the top panel of Fig 3.35, but is primarily a run-dependent global
scale factor on energy. Finally the radial- and energy- dependent energy correction
(3.3.4.3) are indeed correlated and therefore treated multidimensionally ($R,E$).}\\
\textcolor{green}{Rpahael: I believe Nathan will provide answer more detailed 
for this.  If not need to be clarified.} \\

37) Fig. 3.39, I am a bit troubled by the huge shift in missing energy - on 
average several 100 MeV - after applying the corrections. This contrasts to  
Figs. 3.34-3.38, where most deviations from the true pi0 mass appear to be less  
than a couple $\%$.\\
\textcolor{blue}{Most pi0 are found at low energy, while the correction affects
2 to 6.0 GeV photons. This is the reason the correction has such an important 
impact. See later reply to question 31 ii from reviewer 2 for more details.}\\
\textcolor{green}{Raphael: Same as previous.} \\

@@

40) Fig. 4.2: I'm bothered by the wide distribution in Emiss (top middle), and 
don't understand why you use such wide cuts. Surely, anything above Emiss = 0.4 
must have additional particles in it, and even if not, why not cut this tail?  
Note that the same tail is absent for the p (FIg. 4.6) where you use indeed a 
tighter cut, although you don't even account for the proton's initial 
momentum.\\
\textcolor{blue}{ We applied 3$\sigma$ guided by the comparison between data 
and simulation, see figure 4.4 in the note. In the following, figure 
\ref{fig:coherent_ME_bins}, we performed bins in the missing energy 
distribution and we watch the reconstructed beam-spin asymmetries. As a 
conclusion, we see that the reconstructed asymmetries are compatible within the 
given error bars.} \\

\begin{figure}[h!]
   \includegraphics[height=5.0cm]{fig/coh_ME_bins.png}
   \includegraphics[height=5.0cm]{fig/incoh_ME_bins.png}
   \includegraphics[height=5.5cm]{fig/BSA_coherent_ME.png}
   \includegraphics[height=5.5cm]{fig/BSA_incoherent_ME.png}
   \includegraphics[height=5.5cm]{fig/coh_ME_alpha.png}
   \hspace{+0.7cm}
   \includegraphics[height=5.5cm]{fig/incoh_ME_alpha.png}

@@

41) Fig. 4.6: Here you could cut deeper on the ep missing mass. Can be done.
Why is it so lopsided? Because the fact that we do not take into account the 
proton's initial momentum. Didn't you correct the IC photons to avoid that? \\
\textcolor{blue}{We can always cut deeper. We choose not to cut by eye, but 
   using 3 $\sigma$ in order to avoid biassed choices. Moreover, most 
   contamination eventually remaining is pi0 and is treated by a specific 
correction. We do not understand how IC correction can possibly affect the epX 
system.}\\

42) Fig. 4.8: Again, the missing energy from epgamma is lopsided, as is the 
missing egamma mass. Looks like Egamma is still not properly calibrated; but 
then why are the corresponding plots for the coherent channel spot-on? \\
\textcolor{blue}{The assymetry effects are due to the background of the pi0
contributing only on one side of distributions. The peaks are indeed all 
slightly shifted, this is probably due to a complex mix of misalinements and 
miscalibrations. Any attempt to correct with a simple function for one 
variable makes the other worse. In particular, we want to point out that both 
epX and e$\gamma$X missing mass are slightly off but ep$\gamma$ missing mass 
is peaked at 0. These problem do not appear for the coherent channel because
of the larger mass term that reduce the relative impact of some of the
measurement errors. Equation \ref{eq:egamma.} shows that the precision on the 
calculated missing mass squared of $e\gamma X$ depends on the mass of the 
initial state hadron in each DVCS channel.}\\
   \begin{equation}
      \frac{\partial MM^2_{e\gamma X}}{\partial E_{\gamma}}
      = 2*(E_{\gamma^{*}}-M_{target} - E_{\gamma})
      \label{eq:egamma}
   \end{equation}

>>>>

1) Eq. 2.1, p.16: The second row is missing the charge, q, in front of Bz. This 
is not trivial, as the next 3 lines contain numerical examples that seem to be 
wrong. For instance, the range in $r_{0}$ quoted for DVCS is 20 - 45 mm - but I 
find a radius of 100 mm for 260 MeV/c 4He nuclei going radially (q = 2e). Even 
at some angle, 20 mm is impossible - such a track would never make it through 
the drift region. (Fig. 2.7 shows a minuscule pedestal below $r_{0}$ = 25 mm, but 
this must be due to some spurious effect - I don't see how you can reconstruct 
any tracks with $r_{0}$ < 30 mm). Is this mistake in your software as well (see 
horizontal scale in Fig. 2.7)?\\
\textcolor{blue}{
   In equation 2.1, the charge of the particle (q) is indeed missing. Regarding the 
numerical calculations of $r_0$ for the elastic and the DVCS $^4$He, the 0.3 
factor is missing only in these calculations while the charge issue is taken 
into account. In the reconstruction software, both issues are properly 
implemented. (For example, In a magnetic field of 4.5 T, the recoil 4He nuclei 
from DVCS (elastic) reaction have kinetic energies in the range [10, 25] ([17, 
35]) MeV, from momenta of [260, 450] ([360, 550]) MeV and $r_0$ [70, 150] 
([130,180]) mm.) }\\

2) Section 2.2: The RTPC calibration procedure is described in 2 steps: Event 
selection (2.2.1) and actual calibration (2.2.2 - 2.2.4) plus noise rejection 
(2.2.5). However, the event selection contains cuts on $r_0$, chi2, z etc.  
which in turn presuppose some initial calibration already. In other words, the 
process MUST be iterative - but I couldn't find a clear summary how this 
iteration was executed (i.e., what was used for the first iteration, how many 
iterations total, etc.). There is a short mention at the bottom of p. 27, but 
no details.\\
\textcolor{blue}{The drift paths and drift speed were first extracted using the 
MAGBOLTZ Monte Carlo simulation. One can find the detailed procedure of 
a similar extraction in the BoNuS analysis note 
(https://www.jlab.org/Hall-B/secure/bonus/publication/BonusAnal110117.pdf).  
Then, we proceeded to derive empirical improvements with many iterations after 
each change that would affect the drift paths, such as the beam-offset
 and gain calibrations of the RTPC. Moreover after each pass, the number of
elastic events used for calibration increased. Overall, this was a long 
process that evolved and improved over the years and we concentrated in the 
note on the description of the final iteration.}\\

3) 2.2.1.1 It would be helpful to have some more background information: What 
is the longest drift time (from the inner radius) for a good track? What kind 
of momentum gives you only 4 hits, and are those events important? (see further 
down, under Fig. 3.19) What is the timing offset between the trigger and the 
shortest drift time (outer radius RTPC)? What is the average drift velocity and 
Lorentz angle? Conversion TDC-> time is given p. 15, but it would be much more 
helpful to have all these basic parameters collected in a single place: 2.1.1 - 
2.1.3 are all good places to summarize these parameters.\\
\textcolor{blue}{
  The longest drift time depend on $z$ but is typically around 6.6 $\mu$s. 
  Four is the number of the active pads for a track, not the number of hits.  
  This value has been found to be reasonable from simulation, it mainly help 
  clean the sample and plays very little role after other cuts. The time offset 
  is 15 TDCs (1 TDC= 114 ns), the average drift velocity is 6.14 $\mu$m/ns and 
  we did not extract the Lorentz angle, but MAGBOLTZ indicated about 20 
  degrees.}\\

@@

5) 4th bullet: How are the points $r^{helix}$, $\phi^{helix}$ and $z^{helix}$ 
determined?  Somehow, you have to identify points on a continuous line that are 
closest to (perhaps) the hits? How are the uncertainties (sigmas) in  
$\chi^{2}$ determined?  Are those the final values AFTER calibration? If so, 
how do you select your sample initially? (See above - it must be an iterative 
process).  \\
\textcolor{blue}{$(r^{helix},\phi^{helix},z^{helix})$ is the point
on the helix that is closest to the reconstructed hit position.
The values of the uncertainties are intrinsic detector properties depending
primarily on the size and configuration of the readout pads. These 
uncertainties, $(\sigma_{r}, \sigma_{\phi}, \sigma_{z}) = (0.53 mm, 2^{\circ}, 
1.2 mm)$, were not derived from our data and were held fixed over all 
calibration itterations.} \\

\textcolor{blue}{Equation 2.2 needs the beam-spot constraint added in
quadrature $\left(\frac{DOCA}{\sigma_r}\right)^2$ and the denominator adjusted
accordingly $(N_{pts}-4)$. It has to be written in full form as: (changed in 
the note as well).  }\\

\textcolor{blue}{
\begin{equation}
   \chi^{2} = \frac{\displaystyle \left(\frac{DOCA}{\sigma_r}\right)^2 
       + \sum_{i = 1}^{ N_{pts}} \left(\frac{r^{pt}_{i} 
      - r^{helix}_{i} }{\sigma_{r}}\right)^{2}  + \left( \frac{\phi^{pt}_{i} - 
      \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
   z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 4}
\end{equation}
}\\
%  \textcolor{green}{Raph: I did a minor change in the equation, to clarify 
%  that the beam spot term is not in the sum. To use in the note if you are 
%  ok.} \\

@@

14) Figs. 2.20-22: Again, more detail needed to understand what's plotted and 
how it is calculated. Why is Delta-phi not zero for TDC = 15 (which corresponds 
to the outer radius of the drift region)?- Eq. 2.9: A (brief) derivation would 
help a lot here.\\
\textcolor{blue}{
$\Delta \phi$ at the anode (TDC = 15) is not equal to zero because there is a 
drift in $\phi$ between the anode (the first GEM layer at radial distance equal to 
60 mm) and the readout pads (at radial distance equal to 69mm). Regarding the 
derivation, figure \ref{fig:drift_derive} shows a simple drawing explaining how 
Eq. 2.9 has been derived.}\\
\textcolor{green}{Raph: Equations in the drawing need to be replaced by text.}

@@

15) 2.2.4: Eq. 2.12 is differential, while Eq. 2.14 is integrated over the 
whole track. Do you integrate Eq. 2.12? Otherwise, it probably doesn't work all 
that well. Maybe this is the reason why the bands visible in Fig. 2.29 are not 
well represented by the superimposed curves? BTW, what is the vertical scale on 
Fig. 2.29?\\
\textcolor{blue}{Eq. 2.14 represents the average energy loss per unit of length in the 
track, $vtl$ being the visible track length. Assuming the energy loss in the 
drift region small, the two can be easily compared. Indeed at the lowest energy 
this assumption is not true anymore. But the difference between instantaneous 
and average $\frac{dE}{dx}$ is expected to be small compared to our 
resolution except very close to threshold (see right panel of Figure 
\ref{fig:energylosscorrection}).} \\
\textcolor{blue}{In Fig. 2.29 the lines are just there to guide the eye. Since the
vertical scale has never been carefully calibrated, we always present it in
arbitrary units. To have a feeling of the units, we have extracted an over all 
conversions from comparing real data to simulation, where 1 ADC is equal to 17 eV 
(21 eV) deposited in the left (right) module of the RTPC.} \\

16) p. 29, 2nd to last paragraph: I THINK I understand the Landau fit (over 
many tracks, no?) for each channel. But I don't understand the last step - why 
is it needed? What does it accomplish? For sure more details (and a plot) are 
needed.\\
\textcolor{blue}{
Yes, the gain ratio of each readout pad is calculated from comparing all the 
experimental elastic tracks to their corresponding tracks obtained from 
simulation. These ratios give us a first gain for each readout pad. However, 
we noticed that some pads record lower ADCs than expected (issue shown in 
figure 2.28) and sometime noise. For these reasons, we wanted to make sure that the recorded 
ADCs by a given pad are similar to the recorded ADCs recorded by another pad in 
the same track. In figure~\ref{fig:dedxre}, one can see improvements obtained
by using this method to fine tune the gains obtained previously.} \\

\begin{figure}[!h]
\hspace{-0.5 cm}
\includegraphics[height=11.5cm]{fig/dedx_ratio_elastic_NAB.png}
\caption{The ratio between the experimental dEdx and the simulated ones for 
   different regions along $z$ of the RTPC. The blue lines are using the first 
   method of extracting the gains (comparing the experimental recorded dEdx to 
   the expected values calculated from the Bethe-Block formula), the green 
lines are using the 1st pass of the second method (comparing simulation to data 
only) with all the elastic event sample and the brown lines are using the gains 
extracted from the second method (both steps).}
\label{fig:dedxre}
\end{figure}

@@

26) Fig. 3.15: This may be my ignorance, but it looks like there is a 
secondary 'bump' between beta =0.9 and 1. What could it be? If it's neutrons, 
wouldn't that contribute to your background?\\
\textcolor{blue}{We seem to disagree there is a significant bump. However, if 
   there are some neutrons, they will be highly suppressed by the DVCS
   exclusivity requirements. In particular we want to point out the energy of the 
   neutral particle is always greater than 2 GeV. At such energies the time 
   of flight measurement from the EC is not good enough to separate neutrons 
   from photons anyway (see Fig. \ref{fig:sim_coh} and \ref{fig:sim_incoh}).}\\

27) Bottom p.47: Indicate that the threshold on IC discris towards TDC has been 
too high to be useful and/or the flight path is too short to apply a beta cut 
as in EC.\\
\textcolor{blue}{
 The timing of the IC is not functionning properly for certain channels. Therefore, 
 applying a timing cut would add inefficient regions in the detector that we 
 wanted to avoid. Moreover, the comment from previous answer applies as well,
such a cut would be very little help to reduce backgrounds at such high particle energies.}\\

28) Fig. 3.19:  The lhs of the RTPC apparently has only 1/2 the efficiency of the 
rhs. Is there any good explanation (at least qualitatively)? This could 
potentially distort $phi$-distributions, no? \\
\textcolor{blue}{ 
   This difference in the yield should not be linked to a different performance 
   of the RTPC.  They are due to the complicated convolution of CLAS and the 
   RTPC acceptance.  We measured the efficiency of RTPC using elastic 
scattering, and found that the left/right halves have similar efficiencies 
except near the upstream and downstream ends, as shown in 
Figure~\ref{fig:tpceff}.} \\

@@

\textcolor{blue}{ Regarding the background, figure 
\ref{fig:delta_z_after_exclusitivty} shows $\Delta z$ distributions of the 
identified Coherent DVCS events after applying the exclusivity cuts without any 
initial constrain on $\Delta z$.  This guides us to correct for these 
accidentals in our asymmetries in the form: $ A_{LU~~corr.} = \frac{1}{1 - 
contamination} A_{LU}$ }\\

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/rtpc_delta_z.png}
\caption{The z-vertex correspondence between the scattered electron and the 
recoil He4 for the identified coherent DVCS events after the exclusivity cuts 
in the two modules of the RTPC separately without any initial constrains on 
z-vertices of the individual particles.  Table \ref{table:Events_numbers} 
summarizes the cut numerically.}

\label{fig:delta_z_after_exclusitivty}
 \end{figure}

\begin{table}[!h]
   \centering
   \begin{center}
      \begin{tabular}{|l|l|l|}
         \hline
         \multicolumn{3}{ |c| }{Number of coherent DVCS events} \\
         \hline
         $\Delta z$ [mm] & Left module & Right module\\
         \hline
         [-50:-30] & 42 & 77 \\
         \hline
         [-20:20]  & 2741 & 2856\\
         \hline
         [30:50]   & 34 &  78 \\
         \hline
         Contamination percentage  & 2.7$\%$  & 5.4$\%$ \\
         \hline 
      \end{tabular}
      \caption{The numbers of the identified coherent DVCS events in the 
      different regions in $\Delta z$ for the two modules of the RTPC.}
      \label{table:Events_numbers}
   \end{center}
\end{table}

@@

34) Also in 3.2.5, I would like a little more detail on the fastmc: How does it 
calculate the energy loss of the 4He? Is multiple scattering included? Could 
you show comparisons between measured and simulated distributions?\\
\textcolor{blue}{We do not specifically apply energy loss and multiple 
scattering in our fastmc, but we apply resolution effects based on 
experimental data that include both effects. The plots in Fig.~\ref{fig:comp_He} 
show the comparison between data and simulation in terms of theta, $phi$ and 
momentum of the He-4 DVCS nuclei.}\\

@@

35) 3.3.: The kinematic corrections you mention are based on simulation only and 
mostly take care of energy loss by the protons. Most other CLAS analyses 
require additional, EMPIRICAL kinematic corrections (see, e.g. the BONuS 
experiment). Can you give a justification for leaving them out?
It may be obvious, but you don't show or say it: Are the corrections explained 
in 3.3.1-3.3.3 applied to the real data as well?\\
\textcolor{blue}{For electrons and protons, the presented corrections in 
sections 3.3.1 and 3.3.2, respectively, are applied for experimental data and 
simulation. We did not find the need for additional kinematic corrections on 
protons and electron as we found good enough match already.
In the case of the energy of the IC photons, the corrections 
for data and for simulation are different and presented in the following two 
sections, sections 3.3.3 and 3.3.4. In the latter case
these where empirical corrections.  Additional corrections are not pursued
for the data since data and simulation already agree reasonably well regarding
the quantities that are involved in event selection and asymmetry 
extraction.}\\

36) 3.3.4: The 3 corrections you describe for IC photons are somewhat 
correlated, since they all are checked by optimizing $m_{\pi^0}$. Did you try a 
simultaneous fit of all parameters (or at least several ones) that enter the 
various corrections?\\
\textcolor{blue}{The position correction (3.3.4.2) is derived based on minimizing
$z$-dependence of $m_{\pi^0}$, and is highly uncorrelated with energy 
corrections. The run-dependence (3.3.4.1) is also uncorrelated with energy, as
can be seen in the top panel of Fig 3.35, but is primarily a run-dependent global
scale factor on energy. Finally the radial- and energy- dependent energy correction
(3.3.4.3) are indeed correlated and therefore treated multidimensionally ($R,E$).}\\

37) Fig. 3.39, I am a bit troubled by the huge shift in missing energy - on 
average several 100 MeV - after applying the corrections. This contrasts to  
Figs. 3.34-3.38, where most deviations from the true pi0 mass appear to be less  
than a couple $\%$.\\
\textcolor{blue}{Most $\pi^0$ are found at low energy, while the correction affects
2 to 6.0 GeV photons. This is the reason the correction has such an important 
impact. See later reply to question 31 ii from reviewer 2 for more details.}\\

@@

40) Fig. 4.2: I'm bothered by the wide distribution in Emiss (top middle), and 
don't understand why you use such wide cuts. Surely, anything above Emiss = 0.4 
must have additional particles in it, and even if not, why not cut this tail?  
Note that the same tail is absent for the p (FIg. 4.6) where you use indeed a 
tighter cut, although you don't even account for the proton's initial 
momentum.\\
\textcolor{blue}{ We applied 3$\sigma$ based on the comparison between data 
and simulation, see figure 4.4 in the note. In the following, figure 
\ref{fig:coherent_ME_bins}, we performed bins in the missing energy 
distribution and we watch the reconstructed beam-spin asymmetries. As a 
conclusion, we see that the reconstructed asymmetries are compatible within the 
given error bars.} \\

\begin{figure}[tbp]
   \includegraphics[height=5.0cm]{fig/coh_ME_bins.png}
   \includegraphics[height=5.0cm]{fig/incoh_ME_bins.png}
   \includegraphics[height=5.5cm]{fig/BSA_coherent_ME.png}
   \includegraphics[height=5.5cm]{fig/BSA_incoherent_ME.png}
   \includegraphics[height=5.5cm]{fig/coh_ME_alpha.png}
   \hspace{+0.7cm}
   \includegraphics[height=5.5cm]{fig/incoh_ME_alpha.png}

@@

41) Fig. 4.6: Here you could cut deeper on the ep missing mass.
Why is it so lopsided? Didn't you correct the IC photons to avoid that?  \\
\textcolor{blue}{We can always cut deeper. We choose not to cut by eye, but 
   using 3 $\sigma$ in order to avoid biassed choices. Moreover, most 
   contamination eventually remaining is pi0 and is treated by a specific 
correction. We do not understand how IC correction can possibly affect the epX 
system.}\\

42) Fig. 4.8: Again, the missing energy from epgamma is lopsided, as is the 
missing egamma mass. Looks like Egamma is still not properly calibrated; but 
then why are the corresponding plots for the coherent channel spot-on? \\
\textcolor{blue}{The assymetry effects are due to the background of the pi0
contributing only on one side of distributions. The peaks are indeed all 
slightly shifted, this is probably due to a complex mix of misalinements and 
miscalibrations. Any attempt to correct with a simple function for one 
variable makes the other worse. In particular, we want to point out that both 
epX and e$\gamma$X missing mass are slightly off but ep$\gamma$ missing mass 
is peaked at 0. These problem do not appear for the coherent channel because
of the larger mass term that reduce the relative impact of some of the
measurement errors. Equation \ref{eq:egamma} shows that the precision on the 
calculated missing mass squared of $e\gamma X$ depends on the mass of the 
initial state hadron in each DVCS channel.}\\
   \begin{equation}
      \frac{\partial MM^2_{e\gamma X}}{\partial E_{\gamma}}
      = 2*(E_{\gamma^{*}}-M_{target} - E_{\gamma})
      \label{eq:egamma}
   \end{equation}
